A paradigm for \earlywarning\ detection of compact binary coalescence in the context of multi-messenger astronomy

### 2011-06-29 introduction.tex
Reworded caveat in section 1.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1206 ccdd05d5-56c1-461a-bf98-85f6876523b4

We emphasize that Figure~\ref{fig:earlywarning} provides only the lower bound
for early detection and should serve as a baseline to understand the potential
of early warning \GW{} searches in a ideal world.  Real analysis will have
sources of latency that are unavoidable meaning that the actual detection will
occur with some delay.

>>>>

We emphasize that any practical \GW\ search will include technical delays due
to light travel time between the detectors, science infrastructure, and the
selected data analysis strategy.  Figure~\ref{fig:earlywarning} must be understood
in the context of all of the potential sources of latency, some of which are avoidable
and some of which are not.
